\documentclass[.../main.tex]{subfiles}

\begin{document}
	
	In the following chapters, we describe our proposed lines of research which aims
    to study the evolution of swarm systems with independent,
    learning agents under the influence of predictive controls. We
    detail the novel lines of research which this work aims to
    undertake, providing suggestions of the hypotheses posed by
    these lines. With this in mind the following studies are
    proposed and developed subsequently:

    \begin{enumerate}
		\item \textbf{Stability and Chaos in MARL:} in which we seek to understand the dynamics of agent
		strategies when using Q-Learning to learn a game through iteration. We will establish the
		stability, as a function of parameters, when learning general p-player N-action games.  This
		study enables the appropriate selection of parameters and payoff matrices to ensure the
		stability of the strategies of a finite set of agents, such as leaders in a swarm.
        \item \textbf{Dynamics of Mean-Field Q-Learning Games:} in which we examine the
		strategy dynamics for large populations of agents learning through iterated games and
		mean-field Q-Learning. We seek to understand the long term behaviour of such mean-field
		systems in terms of its strategy selection. This study extends the previous and allows for
		the stability of the strategies of a population of agents to be established.
		\item \textbf{Model Predictive Control of Active Particles through Fields:} in which we
		investigate the interaction of a swarm of active particles with potential fields. We
		establish the stabilisability of an MPC scheme with defined stage costs, as well as an
		analysis of the suboptimality of the method.
		\item \textbf{Incorporation of Intelligence in Control:} in which we adapt the dynamical
		system from the above point to include an interaction term, accounting for strategy
		selection by agents who learn through iterated games against one another. Interactions with
		an MPC scheme is then to be examined in a similar capacity. 	 
    \end{enumerate}

    The remainder of this report analyses each of these topics in turn, providing
    motivation and suggestions for the course of research. The first of these `Stability and
    Chaos in MARL' is currently being studied and so is given its own Chapter (Chapter 
    \ref{ch::ShortTermGoals}) which includes a summary of the research.



\end{document}