\documentclass[.../main.tex]{subfiles}

\begin{document}
    
	This chapter outlines a tentative timeline of the research
        described thus far. The numbers in brackets denote the
        estimated months of the PhD that these are likely to take
        place with zero being the beginning of the PhD (October 2019)
        and 48 marking the end (September 2023). Note that there is a
        period of six months at the end which exists to allow for a
        margin of error.


	\begin{enumerate}
		\item Characterisation of Complex Dynamics in Reinforcement Learning Games (for submission
		to AAAI 2021) (\textbf{9 - 12})
		\begin{itemize}
			\item Determining and plotting a simplified expression for a stability line general
			p-player games using Q-Learning (\textbf{9 - 10}).
			\item Running large scale simulations of Q-Learning games to experimentally verify
			results. (\textbf{9 - 11}).
			\item Characterising the Lyapunov exponent for modes of unstable behaviour in Q-Learning
			Dynamics (\textbf{11 - 14})
		\end{itemize}

		\item Control of Swarms with Independent Agents (\textbf{11 - 18})
		\begin{itemize}
			\item Setting up a model predictive control problem for the reduced assumptions of
			particles with no (or limited) interactions (\textbf{11 - 12}) and solving the resulting
			optimisation problem (\textbf{12 - 18}). 
			\item Designing and running simulation code. (\textbf{15 - 18})
		\end{itemize}

		\item Characterisation of the Learning Dynamics of Co-operative Mean Field Games (\textbf{11
				- 18})
		\begin{itemize}
			\item Evaluating the stability of co-operative ($\Gamma = 1$) mean-field games (\textbf{11 - 13})
			\item Evaluating the Lyapunov exponent of the unstable behaviour (\textbf{13 - 16})
			\item Running large scale simulations to verify results (\textbf{15 - 18})
		\end{itemize}

		\item Control of Interacting Swarming Agents (\textbf{19 - 30})
		\begin{itemize}
			\item Setting up and solving MPC optimisation problem on the collisional Vlasov
			equation with short-range interactions between agents. (\textbf{19 - 25})
			\item Designing and running simulation code. (\textbf{24 - 30})
		\end{itemize}

		\item Control of Co-operative Intelligent Swarming Agents (\textbf{28 - 34})
		\begin{itemize}
			\item Setting up and solving MPC optimisation problem on the collisional Vlasov
			equation with augmented interaction term constrained on learning dynamics. (\textbf{28 -
			33})
			\item Designing and running simulation code. (\textbf{32 - 37})
		\end{itemize}

		\item Thesis Completion (\textbf{34 - 48})
		\begin{itemize}
			\item Writing Up (\textbf{34 - 42})
			\item Proof Reading and Editing (\textbf{42 - 44})
			\item PhD Completion (\textbf{44 - 48})
		\end{itemize}

	\end{enumerate}



\end{document}
